Parallel Tractability of Ontology\\ Materialization: Technique and Practice

### 2018-02-01 parallel-tractability-J-v9/background.tex
worked on experimental section, fixed table layout and captions

In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
to denote three disjoint countably
infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
where $R^-$ is the \emph{inverse role} of $R$.
For ease of discussion, we focus on the \emph{simple forms} of axioms shown
in the left column of Table~1. These simple forms can be obtained by using
well-known \emph{structural transformation} techniques \cite{KrotzschRH07,Kazakov09}.

@@

\begin{table}
\begin{center}
\begin{tabular}{lcc}
\multicolumn{3}{c}{\textbf{Table 1: Axioms and corresponding datalog rules}}\\
\hline
&~~~~~~~~~~~~~~~~~~~~~~~~Axioms~~~~~~~~~~~~~~~~~~~~~~~~&~~~~~~~~~~~~~~~~~~~~~~~~Datalog Rules~~~~~~~~~~~~~~~~~~~~~~~~\\
\hline
\hline
(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\

@@

\hline
(A1)& $A(a)$& $A(a)$\\
(A2)& $R(a,b)$& $R(a,b)$\\
\hline
\end{tabular}
\label{tab:dhl}
\end{center}
\end{table}

@@

An ontology
expressed in DHL, DHL($\circ$), DL-Lite$_{\text{core}}$ or DL-Lite$_{\mathcal{R}}$ can be transformed into a datalog program
(see the corresponding rules in the right column of Table~1).
Note that an axiom of form (T4) $A\sqsubseteq\exists R$ should be
transformed into a
first-order logic rule of the form $A(x)\rightarrow \exists y(R(x,y))$, where $y$ is called a \emph{free variable} (it is
not occurring in the body atom $A(x)$).
In this work, such a free variable $y$ is eliminated via Skolemization into a fresh individual $o_{R}^A$
that corresponds to the concept $A$ and the role $R$. The elimination of free variables
does not influence the result of materialization \cite{CalvaneseGLLR07}.

>>>>

In what follows, we use $\textbf{CN}$, $\textbf{RN}$ and $\textbf{IN}$
to denote three disjoint countably
infinite sets of \emph{concept names, role names}, and \emph{individual names} respectively.
The set of roles is defined as $\textbf{R}:=\textbf{RN}\cup\{R^-|R\in\textbf{RN}\}$
where $R^-$ is the \emph{inverse role} of $R$.
For ease of discussion, we focus on the \emph{simple forms} of axioms shown
in the left column of Table~\ref{tab:dhl}. These simple forms can be obtained by using
well-known \emph{structural transformation} techniques \cite{KrotzschRH07,Kazakov09}.

@@

\begin{table}
\centering
\caption{Axioms and corresponding datalog rules}
\begin{tabular}{l >{\hspace*{12mm}}c<{\hspace*{12mm}} >{\hspace*{12mm}}c<{\hspace*{12mm}}}
\hline
& Axioms & Datalog Rules\\
\hline
\hline
(T1)& $A\sqsubseteq B$& $A(x)\rightarrow B(x)$\\
(T2)& $A_1\sqcap A_2\sqsubseteq B$& $A_1(x), A_2(x)\rightarrow B(x)$\\
(T3)& $\exists R.A\sqsubseteq B$& $R(x,y), A(y)\rightarrow B(x)$\\
(T4)& $A\sqsubseteq\exists R$& $A(x)\rightarrow R(x, o_{R}^A)$\\

@@

\hline
(A1)& $A(a)$& $A(a)$\\
(A2)& $R(a,b)$& $R(a,b)$\\
\hline
\end{tabular}
\label{tab:dhl}
\end{table}

@@

An ontology
expressed in DHL, DHL($\circ$), DL-Lite$_{\text{core}}$ or DL-Lite$_{\mathcal{R}}$ can be transformed into a datalog program
(see the corresponding rules in the right column of Table~\ref{tab:dhl}).
Note that an axiom of form (T4) $A\sqsubseteq\exists R$ should be
transformed into a
first-order logic rule of the form $A(x)\rightarrow \exists y(R(x,y))$, where $y$ is called a \emph{free variable} (it is
not occurring in the body atom $A(x)$).
In this work, such a free variable $y$ is eliminated via Skolemization into a fresh individual $o_{R}^A$
that corresponds to the concept $A$ and the role $R$. The elimination of free variables
does not influence the result of materialization \cite{CalvaneseGLLR07}.
